Viscous Transport in Eroding Porous Media

### 2019-07-24 docs/transport/erosion_transport.tex
editing in transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies a Hagen-Poiseuille flow.  The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right].
\end{align}
Initially, $U=1$, and then $U$ is updated at each time step so that the
pressure drop from $x=-2$ to $x=2$ remains constant.  
{\color{red}
We record the flow rate $U$ quantifily in log scale
during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area occupied by bodies is getting smaller $U$ is getting larger.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
with growth rate close to $\ln10^4$. }

\begin{figure}[H]
\center
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
%\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate} The incoming flow rate of $U$ in log scale versus time. 
Under fixed pressure drop condition, $U$ will be small initially,
increase when bodies are eroding, and grow exponentially 
to 1 when there is no body in the fluid. }
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity study in the fluid with 
20 nearly touching bodies when the porosity is 62.9 \%.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The largest 10 difference of 
local tortuosity $\tau$ at two neighboring tracers in
 20 nearly touching bodies eroding when the porosity is 62.9 \% 
and the tortuosity is 1.0979. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
%(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
%(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}
{\color{red}
In Fig.~\ref{fig:Eroding20area} we
measure the area occupied by bodies 
during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
all the bodies are vanished completely.}

\begin{figure}[H]
\center
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
%\caption{}
\end{subfigure}%
\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
  touching eroding bodies and the eroding speed versus time. 
}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies a Hagen-Poiseuille flow.  The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right].
\end{align}
Initially, $U=1$, and then $U$ is updated at each time step so that the
pressure drop from $x=-2$ to $x=2$ remains constant.  
{\color{red}
We
measure the area occupied by bodies 
during the eroding and record the flow rate $U$ quantifily in log scale
during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area fraction is getting smaller $U$ is getting larger.
In Fig.~\ref{fig:Eroding20flowrate}, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies initially and the flow rate U starts from $9.86\times 10^{-5}$. 
Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when the area fraction equals 7.57\% 
which is occupied by 8 bodies.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate U increases exponentially 
with growth rate close to $\ln10^4$. }

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20 nearly
 touching eroding bodies and the eroding speed versus time. 
(b) The incoming flow rate of $U$ in log scale versus time. 
Under fixed pressure drop condition, $U$ will be small initially,
increase when bodies are eroding, and grow exponentially 
to 1 when there is no body in the fluid. }
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity study in the fluid with 
20 nearly touching bodies when the porosity is 62.9 \%.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The largest 10 difference of 
local tortuosity $\tau$ at two neighboring tracers in
 20 nearly touching bodies eroding when the porosity is 62.9 \% 
and the tortuosity is 1.0979. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
%(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
%(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}
